High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-09-05 notebooks/circles.qmd
multi-threading for model training

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 32
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden,), 
    σ=activation
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                      # finaliser function
```

@@

```{julia}
# Simple MLP:
mlp = NeuralNetworkClassifier(
    builder=builder, 
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)

@@

# Joint Energy Model:
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=20,
)

>>>>

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 32
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden,), 
    σ=activation
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                      # finalizer function
```

@@

```{julia}
# Simple MLP:
mlp = NeuralNetworkClassifier(
    builder=builder, 
    epochs=epochs,
    batch_size=batch_size,
    finalizer=_finaliser,
    loss=_loss,
)

@@

# Joint Energy Model:
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finalizer=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=20,
)

### 2023-09-05 notebooks/gmsc.qmd
multi-threading for model training

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 250])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy            # loss function
_finaliser =  Flux.softmax                  # finaliser function
```

@@

# Joint Energy Model:
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=30,
)

>>>>

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 250])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy            # loss function
_finaliser =  Flux.softmax                  # finalizer function
```

@@

# Joint Energy Model:
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finalizer=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=30,
)

### 2023-09-05 notebooks/linearly_separable.qmd
multi-threading for model training

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 16
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden), 
    σ=Flux.swish
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                   # finaliser function
```

>>>>

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 16
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden), 
    σ=Flux.swish
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                   # finalizer function
```

### 2023-09-05 notebooks/mnist.qmd
multi-threading for model training

```{julia}
# Model parameters:
epochs = 25
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

@@

# Joint Energy Model:
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=25,
)

@@

# Final model:
lenet = NeuralNetworkClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=50,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

>>>>

```{julia}
# Model parameters:
epochs = 25
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finalizer function
```

@@

# Joint Energy Model:
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finalizer=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=25,
)

@@

# Final model:
lenet = NeuralNetworkClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=50,
    batch_size=batch_size,
    finalizer=_finaliser,
    loss=_loss,
)
```
